Analysis: NAME

### 2021-07-27 gc_fid_data.Rmd
combine Fractions computationally

```{r}
# Recombine Fractions for m0f0 + m0f3 samples
results_m0f0_m0f3 <- results %>% 
  filter(str_detect(sample, "_F")) %>% 
  mutate(frac = case_when(
    str_detect(sample, "F1") ~ "F1",
    str_detect(sample, "F2") ~ "F2",
    str_detect(sample, "F3") ~ "F3")) %>% 
  mutate(
    sample = str_remove(sample, "_F.")) %>% 
  mutate(
    sample = str_remove(sample, "_"))

```{r}
# Combine triplicate samples into one
results_trip <- results %>% 
  # Remove standards and fractions for this
  filter(sample != "FAME37.1") %>% 
  filter(sample != "TCBAME-2") %>% 
  filter(!str_detect(sample, "F1")) %>% 
  filter(!str_detect(sample, "F2")) %>% 
  filter(!str_detect(sample, "F3")) %>% 
  filter(!str_detect(sample, "cr")) %>%
  mutate(sample_rep = str_remove(sample, "[xyz]")) %>% 
  group_by(sample_rep, `Peak Name`) %>%
  # Replace NA Height and Area values with Zero in order to do summarizing operations
  mutate(`Relative Height` = replace(`Relative Height`, is.na(`Relative Height`), 0)) %>%
  mutate(`Relative Area` = replace(`Relative Area`, is.na(`Relative Area`), 0)) %>% 
  # Generate summary stats
  summarize(rel_area_max = max(`Relative Area`),
            rel_area_min = min(`Relative Area`),
            rel_height_max = max(`Relative Height`),
            rel_height_min = min(`Relative Height`),
            `Retention Time` = mean(`Retention Time`),
            `Relative Area` = mean(`Relative Area`),
            `Relative Height` = mean(`Relative Height`)) %>% 
  # Add some basic metadata
  mutate(inc_time = case_when(
    str_detect(sample_rep, "...0") ~ 0,
    str_detect(sample_rep, "...3") ~ 3,
    str_detect(sample_rep, "...7") ~ 7),
    site = case_when(
      str_detect(sample_rep, "c") ~ "GG Conifer",
      str_detect(sample_rep, "t") ~ "NWT Tundra",
      str_detect(sample_rep, "g") ~ "MM Grassland",
      str_detect(sample_rep, "m") ~ "GG Meadow")
  )
```

>>>>

```{r}
# Recombine Fractions for m0f0 + m0f3 samples
results_m0f0_m0f3 <- results %>% 
  filter(str_detect(sample, "_F")) %>% 
  mutate(frac = case_when(
    str_detect(sample, "F1") ~ "F1",
    str_detect(sample, "F2") ~ "F2",
    str_detect(sample, "F3") ~ "F3")) %>% 
  mutate(
    sample = str_remove(sample, "_F.")) %>% 
  mutate(
    sample = str_remove(sample, "_")) %>% 
  # Generate summary statistics with summarize()
  group_by(sample, `Peak Name`) %>% 
  summarize(
    `Retention Time` = mean(`Retention Time`, na.rm=TRUE),
    Area = mean(Area, na.rm=TRUE),
    Height = mean(Height, na.rm=TRUE),
    `Relative Area` = mean(`Relative Area`, na.rm=TRUE),
    `Relative Height` = mean(`Relative Height`, na.rm=TRUE)
  )

# Remove Fraction Data from `results` tbl
results <- results %>% 
  filter(!str_detect(sample, "_F")) %>% 
  bind_rows(results_m0f0_m0f3)
```

```{r}
# Combine triplicate samples into one
results_trip <- results %>% 
  # Remove standards and fractions for this
  filter(sample != "FAME37.1") %>% 
  filter(sample != "TCBAME-2") %>% 
  filter(!str_detect(sample, "F1")) %>% 
  filter(!str_detect(sample, "F2")) %>% 
  filter(!str_detect(sample, "F3")) %>% 
  filter(!str_detect(sample, "cr")) %>%
  mutate(sample_rep = str_remove(sample, "[xyz]")) %>% 
  group_by(sample_rep, `Peak Name`) %>%
  # Generate summary stats
  summarize(rel_area_max = max(`Relative Area`, na.rm=TRUE),
            rel_area_min = min(`Relative Area`, na.rm=TRUE),
            rel_height_max = max(`Relative Height`, na.rm=TRUE),
            rel_height_min = min(`Relative Height`, na.rm=TRUE),
            `Retention Time` = mean(`Retention Time`, na.rm=TRUE),
            `Relative Area` = mean(`Relative Area`, na.rm=TRUE),
            `Relative Height` = mean(`Relative Height`, na.rm=TRUE)) %>% 
  # Add some basic metadata
  mutate(inc_time = case_when(
    str_detect(sample_rep, "...0") ~ 0,
    str_detect(sample_rep, "...3") ~ 3,
    str_detect(sample_rep, "...7") ~ 7),
    site = case_when(
      str_detect(sample_rep, "c") ~ "GG Conifer",
      str_detect(sample_rep, "t") ~ "NWT Tundra",
      str_detect(sample_rep, "g") ~ "MM Grassland",
      str_detect(sample_rep, "m") ~ "GG Meadow")
  )
```
